\documentclass[letterpaper,12pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\input{glyphtounicode}


%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeEducationHeading}[6]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


%---------- RESUME STARTS HERE ----------
\begin{document}


%---------- HEADING ----------
\begin{center}
    \textbf{\Huge \scshape Ramazan Erduran} \\ \vspace{1pt}
    \large
    \textit{Business Intelligence Consultant} \\ \vspace{5pt}
    \small
    \faPhone \hspace{.5pt} \href{tel:905318260538}{+90 531 826 0538}
    $|$
    \faEnvelope \hspace{.5pt} \href{mailto:ramazan.erduran@outlook.com.tr}{ramazan.erduran@outlook.com.tr}
    $|$
    \faMapMarker \hspace{.5pt} \href{}{Ankara, Turkey}
    \\
    \faLinkedinSquare \hspace{.5pt} \href{https://www.linkedin.com/in/ramazan-erduran}{LinkedIn}
    $|$
    \faGithub \hspace{.5pt} \href{https://github.com/AshNumpy}{GitHub}
    $|$
    \faMedium \hspace{.5pt} \href{https://medium.com/@ashnumpy}{Medium}
    $|$
    \faLink \hspace{.5pt} \href{https://ramazan-erduran.super.site/}{Website}
\end{center}

%----------- SUMMARY -----------
\section{Summary}
Dynamic and results-oriented Business Intelligence Consultant with a strong background in data analysis, machine learning, and business intelligence solutions. Highly proficient in leveraging advanced data analytics and Qlik Sense to deliver actionable insights and optimize business operations. Demonstrated expertise in solving complex problems and driving operational efficiencies, with a proven track record of success in both data science projects and consulting environments. Passionate about delivering tailored BI solutions, improving decision-making processes, and supporting clients with innovative, data-driven strategies.



%----------- EDUCATION -----------
\section{Education}
\vspace{3pt}
  \resumeSubHeadingListStart

    \resumeSubheading
    {Hacettepe University}{Ankara, Turkey}
      {B.Sc. in Statistics; \textbf{GPA: 3.12/4.00 - (Honors Graduate)}}{Sep 2018 \textbf{--} Jun 2023}{}{}
      
      \resumeItemListStart
            \resumeItem{Received comprehensive training in Database Management, focusing on database design, query execution, and performance optimization.}
            \resumeItem{Completed an advanced course in Data Mining with R, building statistical models for data analysis and visualization.}
            \resumeItem{Gained hands-on experience with Big Data Analytics tools (KNIME, Spark, H2O), processing and modeling large datasets for actionable insights.}
            \resumeItem{Led a data analysis project using KNIME to predict market trends, which resulted in 10\% improvement in accuracy of market forecasts.}
        \resumeItemListEnd
        
  \resumeSubHeadingListEnd
\vspace{1pt}



%----------- WORK EXPERIENCE -----------
\section{Work Experience}
\vspace{3pt}
    \resumeSubHeadingListStart
        \resumeSubheading
        {BI Technology Qlik Master Reseller}{Istanbul, Turkey}  
        {Business Intelligence Consultant}{Jan 2025 \textbf{--} Current}
        
            \resumeItemListStart
                %\resumeItem{Providing data analytics and business intelligence solutions for SunExpress, one of the leading airlines in the region, leveraging Qlik Sense for reporting and dashboard development.}
                \resumeItem{Leading projects involving data extraction, transformation, and loading (ETL), ensuring high-quality data integration from multiple sources into Qlik Sense applications.}
                \resumeItem{Collaborating closely with business stakeholders to gather requirements and provide actionable insights that support strategic decision-making processes.}
                \resumeItem{Designing and developing comprehensive Qlik Sense dashboards, focusing on business-specific KPIs, enhancing the reporting capabilities of the client.}
                \resumeItem{Handling the end-to-end process of Qlik Sense application deployment, from initial setup to ongoing maintenance and optimization.}
                \resumeItem{Providing technical consultation and recommendations to improve the client's data analytics environment, ensuring the optimal performance of Qlik Sense architecture.}
            \resumeItemListEnd
        \vspace{-15pt}
        \newpage
        \resumeSubheading
        {}{}     
        {Jr. Business Intelligence Consultant}{Jan 2024 \textbf{--} Jan 2025}
        
            \resumeItemListStart
                \resumeItem{Assisted in the design and development of Qlik Sense dashboards for various clients, ensuring data visualizations met business requirements.}
                \resumeItem{Collaborated with senior consultants to analyze business needs and translate them into data-driven solutions using Qlik Sense.}
                \resumeItem{Performed data cleaning and preprocessing tasks, including the extraction, transformation, and loading (ETL) of client data into Qlik Sense.}
                \resumeItem{Contributed to the creation of detailed documentation for Qlik Sense applications and reports, ensuring a clear understanding of project scope and functionality.}
            \resumeItemListEnd
        \vspace{-15pt}
        \resumeSubheading
        {}{}     
        {Technical Consultant}{Aug 2023 \textbf{--} Jan 2024}
        
            \resumeItemListStart
                \resumeItem{Delivering comprehensive software support for Qlik Sense and Qlik NPrinting products, ensuring seamless functionality and user satisfaction.}
                \resumeItem{Managing and optimizing system configurations for Qlik Sense and Qlik NPrinting, contributing to system performance and reliability.}
                \resumeItem{Identifying and resolving complex environmental issues related to TCP/IP, Websocket, Database connectivity, and issues caused by Windows patches, ensuring minimal system downtime.}
            \resumeItemListEnd

    \vspace{10pt}
        \resumeSubheading
        {E-Kalite Yazılım}{Ankara, Turkey}
        {Data Scientist}{Aug 2022 \textbf{--} Oct 2022}
        
            \resumeItemListStart
                \resumeItem{Improved model accuracy and precision by implementing machine learning and deep learning algorithms.}
                \resumeItem{Optimized data analysis processes, resulting in reduced project timelines and increased on-time delivery rates.}
                \resumeItem{Enhanced data processing speed by leveraging Spark for handling large datasets.}
                \resumeItem{Reduced SQL query durations and improved data access performance through optimized database operations.}
                \resumeItem{Supported data-driven decision-making by generating actionable insights through data visualization tools.}
            \resumeItemListEnd
        
        \vspace{-15pt}
        \resumeSubheading
        {}{}     
        {Data Science Intern}{Jun 2022 \textbf{--} Aug 2022}
        
            \resumeItemListStart
                \resumeItem{Developed a machine learning model in Python to predict house prices.}
                \resumeItem{Executed data cleaning, merging, and querying tasks using SQL and Python.}
                \resumeItem{Created interactive data visualizations to support data analysis and reporting.}
            \resumeItemListEnd
    \resumeSubHeadingListEnd



%----------- SKILLS -----------
\section{Skills}
    \vspace{2pt}
    \resumeSubHeadingListStart
    \small{\item{
        \textbf{Programming:}{ Python, R, MySQL, MSSQL, SQLite}
        
        \vspace{5pt}
        \textbf{Technologies (Comfortable With):}{ Git, PySpark, KNIME, Jupyter Notebook, Tensorflow, Scikit-Learn, Numpy, Pandas, Plotly, VS-Code, Markdown, LaTex, RStudio, Qlik Sense, Qlik NPrinting} 
        
        \vspace{5pt}
        \textbf{Technologies (Experienced With):}{ Playwright, Linux, R-Shiny, Minitab, SPSS}

        \vspace{5pt}
        \textbf{Languages:}{ Turkish (Native), English (Professional working proficiency)}
    }}
    \resumeSubHeadingListEnd



%----------- AWARDS & ACHIEVEMENTS -----------
\newpage
\section{Achievements}
\vspace{2pt}
    \resumeSubHeadingListStart
        \resumeSubheading
        {BTK Academy 2023 Datathon}{Best 3\% Competitors $|$ \emph{\href{https://github.com/AshNumpy/BTK-Datathon-2023}{\color{blue}Solution Link}}}{}{}    
        \vspace{-20pt}
        \resumeSubheading
        {TÜPRAŞ 2023 Generation Datathon}{Best 3\% Competitors $|$ \emph{\href{https://github.com/AshNumpy/TUPRAS-Datathon}{\color{blue}Solution Link}}}{}{} 
        \vspace{-20pt}
        \resumeSubheading
        {KPMG Data \& Analytics Challange}{Best 1\% Competitors $|$ \emph{\href{https://github.com/AshNumpy/KPMG-DxA-Analytics-Challange}{\color{blue}Solution Link}}}{}{} 
        \vspace{-20pt}
        \resumeSubheading
        {GDZ Elektrik 2023 Datathon}{Best 10\% Competitors $|$ \emph{\href{https://github.com/AshNumpy/GDZ-Elektrik-Datathon}{\color{blue}Solution Link}}}{}{} 
    \resumeSubHeadingListEnd



%----------- PROJECTS -----------
\section{Projects}
    \vspace{3pt}
    \resumeSubHeadingListStart
        \resumeProjectHeading
        {\textbf{Sales Analysis End to End Machine Learning Project} \
        $|$
        \emph{\href{https://github.com/AshNumpy/Sales-End-to-End-ML-Project?tab=readme-ov-file}{\color{blue}GitHub} 
        $|$
        \href{https://sales-analysis-machine-learning.streamlit.app/}{\color{blue}Web App}}}{}
            \resumeItemListStart
                    \resumeItem{This project is an end-to-end machine learning initiative aimed at analyzing, visualizing, and predicting sales data. The project combines data analysis, business intelligence integration, and machine learning applications to provide valuable insights.}
            \resumeItemListEnd
    
        \resumeProjectHeading
        {\textbf{Analyzing Sleep Quality and Health \& Predicting Stress Level} 
        $|$
        \emph{\href{https://github.com/AshNumpy/Sleep-Health-ML-Project}{\color{blue}GitHub} 
        $|$
        \href{https://sleep-health-ml-project.streamlit.app/}{\color{blue}Web App}}}{}
            \resumeItemListStart
                \resumeItem{The main objectives of the project are to analyze and visualize the data related to health, lifestyle, and demographic factors, derive actionable insights from the visualizations, and predict stress levels of individuals using machine learning techniques.}
            \resumeItemListEnd
      
        \resumeProjectHeading
        {\textbf{All my projects} 
        $|$
        \emph{\href{https://ramazan-erduran.super.site/portfolio}{\color{blue}Website}}}{}
            \resumeItemListStart
                \resumeItem{You can see all my projects and portfolio on my personal website.}
            \resumeItemListEnd
      
    \resumeSubHeadingListEnd



%----------- CERTIFICATES -----------
\section{Certificates}
    \resumeSubHeadingListStart 
        \resumeSubheading
        {Data Science with Python}{Bilgeadam Akademi $|$ \emph{\href{https://github.com/AshNumpy/ashnumpy/blob/main/Certs/Py/bilge_Adam_Data_Science.pdf}{\color{blue}Certificate}}}{}{}    
        \vspace{-20pt}
        \resumeSubheading
        {Data Scientist with Python}{Datacamp $|$ \emph{\href{https://www.datacamp.com/statement-of-accomplishment/track/eb7026e17d8e342625b5c4d58013614d16dbf231}{\color{blue}Certificate}}}{}{} 
        \vspace{-20pt}
        \resumeSubheading
        {All My Certificates}{On My Github $|$ \emph{\href{https://github.com/AshNumpy/ashnumpy/blob/main/Certs/README.md}{\color{blue}Certificate}}}{}{} 
        \vspace{-20pt}
    \resumeSubHeadingListEnd



%----------- ORGANIZATIONS -----------

% \section{Organizations}
  % \resumeSubHeadingListStart
    
    % \resumeOrganizationHeading
      % {Institute of Electrical and Electronics Engineers (IEEE)}{Feb 2022 -- Present}{Student Member}
    
  % \resumeSubHeadingListEnd



%----------- HOBBIES -----------

% \section{Hobbies}
  % \resumeSubHeadingListStart
    % \small{\item{Swimming, Fitness, Eight-ball}}
  % \resumeSubHeadingListEnd



%----------- REFERENCES -----------

% \section{References}
  % \resumeSubHeadingListStart
    
  % \resumeSubHeadingListEnd



%-------------------------------------------
\end{document}